---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Sourav Gupta"
date: "25-09-2023"
format: html
editor: visual
self-contained: true
---

```{r}
install.packages("DataExplorer")
```

```{r}
install.packages("magrittr")
install.packages("tidyverse")
install.packages("tidymodels")
install.packages("gt")
install.packages("gtExtras")
install.packages("DataExplorer")
```

```{r}
library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
```

## Setup

Load packages and data:

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

## Exercises

```{r load-pkg-data}

 
# Load the required libraries 
library(dplyr) 
library(readr) 
# Load the datasets 
the_tate <- read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE) 
the_tate_artists <- read_csv("data/the-tate-artists.csv")
print(the_tate) 
# Calculate the number of unique artists represented in the collection 
unique_artists_count <- the_tate_artists |>   distinct(name) |>   nrow() 
# Number of rows and columns in the the_tate dataset 
tate_dimensions <- dim(the_tate) 
# Summary statistics of the the_tate dataset 
tate_summary <- the_tate |>   summarize(     TotalArtworks = n(),               
# Total number of artworks    
UniqueArtists = unique_artists_count, 
# Number of unique artists     
MinYear = min(year, na.rm = TRUE),  
# Minimum year in the collection   
MaxYear = max(year, na.rm = TRUE), # Maximum year in the collection  
MinacquisitionYear = min(acquisitionYear, na.rm = TRUE),   
MaxacquisitionYear = max(acquisitionYear, na.rm = TRUE)
)
# Print the summary 
print(tate_summary)

```

## Exercise 1

The `the_tate` dataset has *3526* unique artists who worked from 1545 to 2012. The works were acquired between the years 1823 and 2013.

### Exercise 2

How number of works with missing dates is \_\_.

The number of artists whose works have missing dates is \_\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_\_\_\_.

### Exercise 3

The artist with the most works in the Tate collection is \_\_\_.

The artist with the tenth-most works in the Tate collection is \_\_\_.

### Exercise 4

The artist with the greatest number of works in the Tate collection represent \_\_\_% of the total number of works

### Exercise 5

There are \_\_ duplicate artist-title pairs

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
